\subsubsection{Variable Names}
\begin{itemize}[--] %http://en.wikibooks.org/wiki/LaTeX/List_Structures
	\item Internal variables
		\begin{itemize}
			\item Internal variables are local to the function it is declared in. 
			\item They can have a can have a length of 31 characters and can only be comprised of integers and letters and numbers (The underscore counts as a letter). 
		\end{itemize}

	\item External variables
		\begin{itemize}
			\item External variables (globals) are variables that exist for all functions. 
			\item External names can only have a length of 6 characters and one case because they may be used by assemblers and loaders.
		\end{itemize}

	\item Variable naming good practice
		\begin{itemize}
			\item You shouldn't start off variables with an underscore because library routines often use those names. 
			\item It is traditional practice to use lower case for variable names, all uppercase for symbolic constants and a capitalized name for object types. 
		\end{itemize}
\end{itemize}


\subsubsection{Data Types and Sizes}
\begin{description} 
	\item[char] a single byte, 8 bits
	\item[int] an integer, size depends on system
	\item[short] an integer that is no larger than an integer (typically 16 bits)
	\item[long] an integer, size is no smaller tahn an int (typically graeter than or equal to 32 bits)
	\item[float] single-precision floating point
	\item[double] double precision floating point
	\item[unsigned (data type)] respective data type that can only be greater than or equal to 0. Because there are no negative numbers, one can have much more positive numbers ($maxSignedNumber * 2 + 1$) 
\end{description}


\subsubsection{Constants}
\begin{itemize}[--]
	\item An integer constant can be represented like as just an int, hexadecimal, decimal or octal: 1234
	\item A long constant is represented as a short constant with a terminal L or l, or it is a number too big to fit in an int: 123456789l or 123456789L
	\item An unsigned integer constant is represented with a u or U at the end of an integer: 1234u or 1234U
	\item An unsigned long constant is represented as a long but with a ul or UL at the end of the constant: 1234ul or 1234UL
	\item A double constant is represented as a number with a decimal point or as an exponent: 43.1
	\item A float constant is the same representation as a double constant but with a f or F suffix: 43.1F or 43.1f
	\item A character constant is an integer written as one character within single quotes such as `f'. Certain characters can be represented by escape
		  sequences. Below is the complete set of escape sequences:
	\begin{tabular}{c | c || c | c}
		\hline 
		a & alert(bell) character & \ & backslash
		b & backspace &? & question mark
		f & formfeed & ' & single quotes
		n & newline & " & double quotes
		r & carriage return & ooo & octal number
		t & horizontal tab & xhh & hexadecimal number
		v & vertical tab  & 0 & null character
	\end{tabular}
	
	\item A constant expression is an expression that involves only constants. Such expressions are usually evaluated during compilation rather than at run time
	\item A string constant or string literal is a sequence of zero or more characters surrounded by double quotes: "Something like this"	
	\item An enumeration is a list of constant integer values that can be specified, really similar to #define. two examples of this is: 
		enum boolean {NO, YES}; /*NO = 0, YES = 1*/. similarly enum months{JAN = 1, FEB, MAR, APR, MAY} /*JAN = 1, FEB = 2, MAR = 3*/
\end{itemize}


\subsubsection{Declarations}
\begin{itemize}{--}
	\item All variables must be declared before use. Declarations specify a type and contains a list of one or more variables of that type
	\item Automatic (or internal) cariables are initialized to garbage variables if not explicitely initialized and are initialized every time that block of code is run
	\item External and static variables are initialized to zero by default and are initialized once throughout the life of a program
	\item The qualifier const can be applied to a declared variable and it specifies that the variable will not be changed 
\end{itemize}

\subsubsection{Arithmetic Operators}
\begin{itemize}{--}
	\item The binary operators are +,-,*,/ and the modulus operator \%. Integer division truncates any fractional part. One cannot use \% for float or double types.
\end{itemize}

\
